Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2022-01-03 paper/paper.tex
update paper
update

\begin{table}[h]
\caption{The number of independent sets for square grid graphs of size $L\times L$. This forms the integer sequence \href{https://oeis.org/A006506}{OEIS A006506}.
Here we only show two updated entries for $L=38,39$ that has not been computed before.}
\begin{center}
\scalebox{0.9}{
\begin{tabular}{|c| >{\centering\arraybackslash} p{0.95\linewidth}|}
 \hline $L$  & square grid graphs \\
 \hline $ 29$ & 3 556 619 491 488 838 337 298 644 336 171 591 528 960 687 731 348 622 394 588 805 214 244 031 766 315 339 709 627 465 589 460 212 852 431 000 227 410 783 701 037 177 097 019 793 172 369 009 198 594 591 \\
 \hline $ 30$ &  112 377 766 778 527 126 203 646 648 402 050 958 984 330 252 199 994 469 198 044 986 979 798 657 215 652 532 005 142 877 926 040 203 499 014 641 860 333 039 219 325 350 361 465 468 647 055 420 204 598 509 312 491 705 \\
  \hline
\end{tabular}
}
\end{center}
\label{tbl:squaregrid}
\end{table}

@@

We also computed independence polynomial rigorously for these lattices in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{Github repo}.

>>>>

We computed the number of independent sets on square lattices and King's graphs
with our generic tensor network contraction on GPUs.
The tensor element type is finite field algebra so that we can reach arbitrary precision.
We also computed independence polynomial rigorously for these lattices in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{Github repo}.

\begin{table}[h]
\caption{The number of independent sets for square grid graphs of size $L\times L$. This forms the integer sequence \href{https://oeis.org/A006506}{OEIS A006506}.
Here we only show two updated entries for $L=38,39$, which to our knowledge, has not been computed before.~\cite{Butera2014}
}
\begin{center}
\scalebox{0.9}{
\begin{tabular}{|c| >{\centering\arraybackslash} p{0.95\linewidth}|}
 \hline $L$  & square grid graphs \\
 \hline $38$ & 616 412 251 028 728 207 385 738 562 656 236 093 713 609 747 387 533 907 560 081 990 229 746 115 948 572 583 817 557 035 128 726 922 565 913 748 716 778 414 190 432 479 964 245 067 083 441 583 742 870 993 696 157 129 887 194 203 643 048 435 362 875 885 498 554 979 326 352 127 528 330 481 118 313 702 375 541 902 300 956 879 563 063 343 972 979\\
 \hline $39$ &  29 855 612 447 544 274 159 031 389 813 027 239 335 497 014 990 491 494 036 487 199 167 155 042 005 286 230 480 609 472 592 158 583 920 411 213 748 368 073 011 775 053 878 033 685 239 323 444 700 725 664 632 236 525 923 258 394 737 964 155 747 730 125 966 370 906 864 022 395 459 136 352 378 231 301 643 917 282 836 792 261 715 266 731 741 625 623 207 330 411 607\\
  \hline
\end{tabular}
}
\end{center}
\label{tbl:squaregrid}
\end{table}
% online digit seperator: https://www.browserling.com/tools/thousands-separator

@@
